### 2014-06-04 writing/S'14 paper/recursion.tex
Proofed sec. 4

% TODO: Cite Chomsky/Hauser/Fitch? -- no, not appropriate here --- CP.

@@

The performance of the RNTN model on small unseen test examples
indicates that it learned a correct approximation of the underlying
logic. It appears that this approximation is accurate enough to yield
correct answers when the composition layer is only applied a small
number of times, but that the error in the approximation grows with
depth, resulting in the gradually dropping performance. This is not
necessarily a significant flaw in the model, since it remains possible
that a less lossy approximation of the same logic would do no better
on the training objective, since that objective only considers short
strings and includes a regularization term. Whether a more accurate
encoding could be learned from a larger set of training data remains a
quention for future work. In contrast, the RNN model did not appear to
be able to learn a correct approximation of the logic.

>>>>

@@

The performance of the RNTN model on small unseen test examples
indicates that it learned a correct approximation of the underlying
logic. It appears that this approximation is accurate enough to yield
correct answers when the composition layer is only applied a small
number of times, but that the error in the approximation grows with
increasing depth (and with the increasing complexity of the expressions),
 resulting in the gradually dropping performance. This is not
necessarily a significant flaw in the model, since it remains possible
that a less lossy approximation of the same logic would do no better
on the training objective, since that objective only considers short
strings and includes a regularization term. Whether a more accurate
encoding could be learned from a larger set of training data remains a
quention for future work. In contrast, the RNN model did not appear to
be able to learn a correct approximation of the logic.
